Visualization of [fulle name] Fractional Integrals

### 2019-03-26 fractional/CMJ style files/article-template.tex
edited introduction again

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}
%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
\noindent
Fractional-order calculus can be summarized as the generalization of integer-order differentiation and integration to an arbitrary order. Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$. Leibniz mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he answers the following question posed by L'Hospital: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful 
consequences will be drawn}.'' It can, therefore, be argued that fractional-order calculus is as old as classical calculus itself. In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional 
integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].

It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
interpretation of the fractional integral. Interestingly in 1974, this had alreaady been the state of affairs for more than 300 years []. Subsequently, the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
geometric interpretations and ecenomic interpretations of the fractional integral.

In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is especially useful from 
a pedigogical point of view as it is similar in nature to the definition of classical integration. In ordinary integration we can interpret the integral 
as an infinite sum of rectangular infinitesimals. In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted 
as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.

>>>>

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}
%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
\noindent
Leibniz, who is regarded by many scholars as the farther of calculus, is credited with inventing the following notation: $\frac{d^n y}{d x^n}$. 
A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
In a letter Leibniz sent to L'Hospital, he himself commented on this intriguing question: ``\emph{This is an apparant paradox from which, one day, useful 
consequences will be drawn}.''

It is, however, Liouville and Riemann who laid the theoretical groundwork which was needed to develop the field of fractional calculus. 
Their contribution played a crucial part in defining what is now known as the Riemann-Lioville fractional integral. Fractional calculus can be 
formally defined as the study of a an arbitrary order differentiation and integration operators.

Fractional calculus can be summarized as the generalization of integer-order differentiation and integration to an arbitrary order.
Fractional-order calculus is as old as classical calculus itself. In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional 
integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].

It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
interpretation of the fractional integral. Interestingly in 1974, this had already been the state of affairs for more than 300 years []. Subsequently, the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
geometric interpretations, physical interpretations and ecenomic interpretations of the fractional integral.

In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is especially useful from 
a pedigogical point of view as it is similar in nature to the definition of classical integration. as an infinite sum of rectangular infinitesimals. In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted 
as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$. Furthermore, please note that the intended audience of this 
paper is undergraduate students and lecturers and as such we do not present .  In ordinary integration we can interpret the integral
